---
title: "Fetch"
author: "Yuteng Gao"
date: "2023-02-04"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
library(sqldf)
library(dplyr)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
users <- read_csv("https://github.com/BobbigGao/Fetch/releases/download/Dataset/users.csv")
receipts <- read_csv("https://github.com/BobbigGao/Fetch/releases/download/Dataset/receipts.csv")
receipt_items <- read_csv("https://github.com/BobbigGao/Fetch/releases/download/Dataset/receipt_items.csv")
brands <- read_csv("https://github.com/BobbigGao/Fetch/releases/download/Dataset/brands.csv")
```

# What is the name of the most expensive item purchased?

```{r}
# create a new column called unit price in receipt_items
receipt_items <- sqldf(
  "
  SELECT *,
  `TOTAL_FINAL_PRICE` / `QUANTITY_PURCHASED` AS `UNIT_PRICE`
  FROM receipt_items
  "
)

# find the name of the most expensive item
name <- sqldf(
"
SELECT `Description` 
FROM receipt_items
WHERE `UNIT_PRICE` = (SELECT MAX(`UNIT_PRICE`) FROM receipt_items)
LIMIT 1
")

print(name)
```

The name of the most expensive item purchased is Starbucks Iced Coffee Premium Coffee Beverage Unsweetened Blonde Roast Bottle 48 Oz 1 Ct. However, it is clear that a starbucks coffee can not be that expensice and this receipt is rejected by fetch review. The actual most expensive item should be rewarded the points (i.e. "POINTS_EARNED" in receipt_items is not N/A) and the record should also pass the fetch review.

```{r}
cleaned_receipt_items <- receipt_items[!is.na(receipt_items$POINTS_EARNED),]
cleaned_receipts <- receipts[!is.na(receipts$FINISHED_DATE),]
```

Then using the cleaned dataset, we find the most expensive item that passed fetch review is an universal unknown item. 

# What user bought the most expensive item?

```{r}
# find the receipt ID of the most expensive item
most_exp_receipt_id <- sqldf(
"
SELECT `REWARDS_RECEIPT_ID` 
FROM receipt_items
WHERE `UNIT_PRICE` = (SELECT MAX(`UNIT_PRICE`) FROM receipt_items)
LIMIT 1
")

most_exp_receipt_id <- "6140bb490a720f971f01b2d0"

# find the user ID of this receipt


most_exp_user_id <- sqldf(sprintf("
SELECT `USER_ID` 
FROM receipts
WHERE `ID` = '%s'
LIMIT 1
", most_exp_receipt_id))

print(most_exp_user_id)
```

The user who purchased the most expensive item has the user ID: 609ab37f7a2e8f2f95ae968f. This user is the user who purchased the universal unknown item.


```{r}
cleaned_receipts <- receipts[!is.na(receipts$STORE_NAME),]
brand_counts <- cleaned_receipts %>%
  group_by(STORE_NAME) %>%
  summarize(count = n())
```



